---
title: 12 Days of Scrollable Christmas
format:
  closeread-html:
    debug-mode: false
    remove-header-space: true
    cr-style:
      narrative-background-color-overlay: "#b22222" # Festive red for the overlay background
      narrative-text-color-overlay: "#ffffff"      # White text for contrast
      narrative-font-family: "Georgia, serif"      # Elegant serif font
      narrative-font-size: "20px"                  # Readable size
      narrative-border-radius: "10px"              # Slightly rounded corners
      section-background-color: "#006400"          # Deep green for the section background
      narrative-sidebar-width: "1fr"               # Default width for sidebar
      narrative-text-color-sidebar: "#ffffff"      # White text in sidebar layouts
      narrative-background-color-sidebar: "#b22222" # Matching red for sidebar layouts
---

:::{.cr-section layout="overlay-center"}

## The 12 Days of Scrollable Christmas

The "12 Days of Christmas" is a beloved carol that describes a series of gifts given over twelve days. This interactive scrollytelling experience visualizes each day.<br><br> Built with [Closeread](https://closeread.dev/)<br><br> Published for free on [Posit Connect Cloud](https://connect.posit.cloud/)

### Day 1: A Partridge in a Pear Tree

:::{.cr-section layout="overlay-center"}
:::{.trigger focus-on="day1-sticky"}
On the first day of Christmas, my true love gave to me: a partridge in a pear tree.
:::
:::{#cr-sticky .sticky}
```{r}
library(ggplot2)
ggplot(data.frame(x = c(1, 2, 3, 4, 5), y = c(2, 4, 1, 8, 7)), aes(x, y)) +
  geom_point(color = "gold", size = 5) +
  labs(title = "A Partridge in a Pear Tree", x = "Pear Trees", y = "Partridges") +
  theme_minimal()
```
:::
:::

### Day 2: Two Turtle Doves

:::{.cr-section layout="overlay-center"}
:::{.trigger focus-on="day2-sticky"}
On the second day of Christmas, my true love gave to me: two turtle doves.
:::
:::{#day2-sticky .sticky}
```{r}
ggplot(data.frame(x = c(1, 2), y = c(3, 6)), aes(x, y)) +
  geom_bar(stat = "identity", fill = "blue") +
  labs(title = "Two Turtle Doves", x = "Doves", y = "Count") +
  theme_minimal()
```
:::
:::

### Day 3: Three French Hens

:::{.cr-section layout="overlay-center"}
:::{.trigger focus-on="day3-sticky"}
On the third day of Christmas, my true love gave to me: three French hens.
:::
:::{#day3-sticky .sticky}
```{r}
ggplot(data.frame(x = c("Hen 1", "Hen 2", "Hen 3"), y = c(5, 7, 6)), aes(x, y)) +
  geom_col(fill = "red") +
  labs(title = "Three French Hens", x = "Hens", y = "Performance") +
  theme_minimal()
```
:::
:::



:::{.cr-section layout="overlay-center"}
:::{.trigger focus-on="dayn-sticky"}
On the final day of Christmas, my true love gave to me: three French hens.
:::
:::{#day3-sticky .sticky}
```{r fig.width = 8, fig.height=6}
# Load necessary libraries
library(ggplot2)
library(stringr)  # For text wrapping


# Data preparation
days <- 1:12
gifts_per_day <- c(1, 3, 6, 10, 15, 21, 28, 36, 45, 55, 66, 78)  # Cumulative gifts
lyrics <- c("A Partridge in a Pear Tree",
            "Two Turtle Doves",
            "Three French Hens",
            "Four Calling Birds",
            "Five Gold Rings",
            "Six Geese a-Laying",
            "Seven Swans a-Swimming",
            "Eight Maids a-Milking",
            "Nine Ladies Dancing",
            "Ten Lords a-Leaping",
            "Eleven Pipers Piping",
            "Twelve Drummers Drumming")
wrapped_lyrics <- str_wrap(lyrics, width = 10)



data <- data.frame(
  Day = factor(days, levels = days),
  Gifts = gifts_per_day,
  Lyric = wrapped_lyrics
)

# Define Christmas-inspired colors
christmas_colors <- c("#FF0000", "#008000", "#FFD700", "#FF4500", "#228B22", "#B22222",
                      "#32CD32", "#FF6347", "#006400", "#CD5C5C", "#98FB98", "#8B0000")

# Plot
ggplot(data, aes(x = Day, y = Gifts, fill = Day)) +
  geom_bar(stat = "identity", color = "black", show.legend = FALSE) +
#   geom_label(aes(label = Gifts), vjust = -1, color = "white", size = 5) +
  geom_label(aes(label = Lyric), vjust = 0.5, hjust = 0.5, color = "white", size = 3) +
  scale_fill_manual(values = christmas_colors) +
  labs(
    title = "78 Cumulative Gifts in the '12 Days of Christmas'",
    x = "Day",
    y = NULL ) +
  theme_minimal(base_size = 15) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.text.y = element_text(face = "bold"),
    legend.position = "none"
  )


```
:::
:::


